Draft-assinment1

### 2017-02-20 Draft-xuezhou-sjb.Rmd
delete pngs and fix goals

#Table of Contents
* 1.[Introduction](#Introduction)

* 2.[Goal](#Goal)

College is an investment. It's well-known that a major motivation for students to attend a university is higher post-graduation earning. So will your school make sure you get a return? With collge costs and student-debt levels reaching an all-time high, it's important to know which schools produce the highest earning alumni and what factors can help us predict post-graduate earnings for students in a university.

* 3.[Dataset Preparation](#dataprep)
* 4.[Objective](#objective)
* 5.[Summary of variables](#variablesummary)
* 5.1 [Individual variable summary](#5.1)
  * 5.1.1 [School](#5.1.1)
    * 5.1.1.1 [State](#5.1.1.1)
    * 5.1.1.2 [Predominant Degree](#5.1.1.2)
    * 5.1.1.3 [Control of Institution](#5.1.1.3)
  * 5.1.2 Student Body
    * 5.1.2.1 [Percentage first-generation students](#5.1.2.1)
    * 5.1.2.2 [Number of applications](#5.1.2.2)
  * 5.1.3 Cost 
    * 5.1.3.1 [Average net price for Title IV institutions(both public and private institutions)](#5.1.3.1)
    * 5.1.3.2 [Percentage of students who are financially independent](#5.1.3.2)
  * 5.1.4 Financial Aid
    * 5.1.4.1 [Percentage of undergraduates who receive a Pell Grant](#5.1.4.1)
    * 5.1.4.2 [Percent of all federal undergraduate students receiving a federal student loan](#5.1.4.2l)
    * 5.1.4.3 [The median debt for students who have completed](#5.1.4.3)
    * 5.1.4.4 [The median debt for students who have not completed](#5.1.4.4)
  * 5.1.5 Earning
    * 5.1.5.1 [Median family income in real 2015 dollars](#5.1.5.1)
    * 5.1.5.2 [Earning after graduation](#5.1.5.2)
  * 5.1.6 Repayment
    * 5.1.6.1 [3-year Repayment rate](#5.1.6.1)
    * 5.1.6.2 [3-year Default rate](#5.1.6.2)
* 6.Relationship between variables
 * 6.1 [The relationship between NPT4_COMBINE and State](#6.1)
 * 6.2 [The relationship between Debt and Cost](#6.2)
 * 6.3 [The relationship between Percentage of Pell Grant and college type(CONTROL)](#6.3)
 * 6.4 [The relationship between Percentage first-generation students and States](#6.4)
 * 6.5 [The relationship between family income and percentage of Pell Grant](#6.5)
 * 6.6 [The relationship between DEP_STAT_PCT_IND and Control](#6.6)
 * 6.7 [The relationship between PCTLOAN and Control](#6.7)
 * 6.8 [cost and median debts with earning](#6.8)
 * 6.9 [default with earning](#6.9)
 * 6.10 [degree type vs. earning](#6.10)
 * 6.11 [predominant degree, control  and earning after 6 year of entry](#6.11)
 * 6.12 [predominant degree + control (count)](#6.12)
 * 6.13 [control + earning](#6.13)
* 7. [Findings and Conclusion](#7)

@@

#2. Goal<a id="Goal"></a>
#3. Dataset Preparation<a id="dataprep"></a>
Our analysis focuses on the data of year 2012 -2013 of 23 variables. We chose the median income 6 years after graduation as our predictor variable, and eliminated many fields with bunch of missing values as well as some fields not pertainig enougn to post-graduation income. We then fosued primarily on a set of 23 variables, including gender, age, ethnic, acedemic costs, family income, completetion rates and replayment rate.

>>>>

#Table of Contents
* 1.[Introduction](#Introduction)
* 2.[Goal](#Goal)
* 3.[Dataset Preparation](#dataprep)
* 4.[Objective](#objective)
* 5.[Summary of variables](#variablesummary)
* 5.1 [Individual variable summary](#5.1)
  * 5.1.1 [School](#5.1.1)
    * 5.1.1.1 [State](#5.1.1.1)
    * 5.1.1.2 [Predominant Degree](#5.1.1.2)
    * 5.1.1.3 [Control of Institution](#5.1.1.3)
  * 5.1.2 Student Body
    * 5.1.2.1 [Percentage first-generation students](#5.1.2.1)
    * 5.1.2.2 [Number of applications](#5.1.2.2)
  * 5.1.3 Cost 
    * 5.1.3.1 [Average net price for Title IV institutions(both public and private institutions)](#5.1.3.1)
    * 5.1.3.2 [Percentage of students who are financially independent](#5.1.3.2)
  * 5.1.4 Financial Aid
    * 5.1.4.1 [Percentage of undergraduates who receive a Pell Grant](#5.1.4.1)
    * 5.1.4.2 [Percent of all federal undergraduate students receiving a federal student loan](#5.1.4.2l)
    * 5.1.4.3 [The median debt for students who have completed](#5.1.4.3)
    * 5.1.4.4 [The median debt for students who have not completed](#5.1.4.4)
  * 5.1.5 Earning
    * 5.1.5.1 [Median family income in real 2015 dollars](#5.1.5.1)
    * 5.1.5.2 [Earning after graduation](#5.1.5.2)
  * 5.1.6 Repayment
    * 5.1.6.1 [3-year Repayment rate](#5.1.6.1)
    * 5.1.6.2 [3-year Default rate](#5.1.6.2)
* 6.Relationship between variables
 * 6.1 [The relationship between NPT4_COMBINE and State](#6.1)
 * 6.2 [The relationship between Debt and Cost](#6.2)
 * 6.3 [The relationship between Percentage of Pell Grant and college type(CONTROL)](#6.3)
 * 6.4 [The relationship between Percentage first-generation students and States](#6.4)
 * 6.5 [The relationship between family income and percentage of Pell Grant](#6.5)
 * 6.6 [The relationship between DEP_STAT_PCT_IND and Control](#6.6)
 * 6.7 [The relationship between PCTLOAN and Control](#6.7)
 * 6.8 [cost and median debts with earning](#6.8)
 * 6.9 [default with earning](#6.9)
 * 6.10 [degree type vs. earning](#6.10)
 * 6.11 [predominant degree, control  and earning after 6 year of entry](#6.11)
 * 6.12 [predominant degree + control (count)](#6.12)
 * 6.13 [control + earning](#6.13)
* 7. [Findings and Conclusion](#7)

@@

#2. Goal<a id="Goal"></a>
College is an investment. It's well-known that a major motivation for students to attend a university is higher post-graduation earning. So will your school make sure you get a return? With collge costs and student-debt levels reaching an all-time high, it's important to know which schools produce the highest earning alumni and what factors can help us predict post-graduate earnings for students in a university.

#3. Dataset Preparation<a id="dataprep"></a>
Our analysis focuses on the data of year 2012 -2013 of 23 variables. We chose the median income 6 years after graduation as our predictor variable, and eliminated many fields with bunch of missing values as well as some fields not pertainig enougn to post-graduation income. We then fosued primarily on a set of 23 variables, including gender, age, ethnic, acedemic costs, family income, completetion rates and replayment rate.
